---
title: "Subject Data Analysis"
output: html_notebook
---

# Load Required Libraries
```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(brms)
library(bayesplot)
library(ggplot2)
library(corrplot)
library(ggpubr)
```

# Load Data
```{r load-data}
# Load R.Data file containing modelRT
setwd("~/Documents/MediCoDe-TUS/Behav_TUS/")
subject_data <- read_excel("subject_pressure_data_amcc_pcc_sham.xlsx")

# View the structure of the data
str(subject_data)
head(subject_data)
```


```{r}
ggpaired(subject_data, x =  "Side", y = "peak_pressure" ,color = "Side",
     line.color = "grey", line.size = 0.3, id = "Subject", 
     facet.by = "Region", short.panel.labs = FALSE)
```

```{r}
# ============================================================
# TUS Dose Calculation
# Based on Nandi et al. (2025): Dose = I_SPPA x DC x SD
# (absorbed dose in J/cm²)
#
# Protocol: 5 Hz theta burst TUS
#   - PRF       : 5 Hz
#   - PRI       : 200 ms
#   - Duty Cycle: 10% (0.10)
#   - Pulse dur : PRI x DC = 200 ms x 0.10 = 20 ms
#   - Sessions  : SD = 2 s and SD = 120 s
# ============================================================


# ------------------------------------------------------------
# STEP 1: Define protocol parameters
# ------------------------------------------------------------

PRF        <- 5          # Pulse repetition frequency (Hz)
PRI_ms     <- 200        # Pulse repetition interval (ms)
DC         <- 0.10       # Duty cycle (unitless, 10%)
pulse_dur_ms <- PRI_ms * DC   # Pulse duration (ms) = 20 ms
pulse_dur_s  <- pulse_dur_ms / 1000  # Convert to seconds

#SD_values  <- c(120)  # Sonication durations to evaluate (seconds)

# Acoustic medium properties (water, used as standard reference)
rho <- 1000              # Density of water (kg/m³)
c   <- 1500              # Speed of sound in water (m/s)
Z   <- rho * c           # Acoustic impedance (Pa·s/m = kg/m²/s)
                         # Z = 1,500,000 Pa·s/m

cat("=== Protocol Parameters ===\n")
cat(sprintf("PRF              : %g Hz\n", PRF))
cat(sprintf("PRI              : %g ms\n", PRI_ms))
cat(sprintf("Duty Cycle       : %g%%\n", DC * 100))
cat(sprintf("Pulse Duration   : %g ms\n", pulse_dur_ms))
cat(sprintf("Acoustic impedance (Z): %.2e Pa·s/m\n\n", Z))
```


```{r}
# ------------------------------------------------------------
# STEP 2: Function — pressure (kPa) to I_SPPA (W/cm²)
# ------------------------------------------------------------
# I_SPPA = P_peak² / (2 × Z)
#
# Where:
#   P_peak  = peak positive pressure in Pa
#   Z       = acoustic impedance in Pa·s/m (= kg/m²/s)
#   Result  = intensity in W/m², then converted to W/cm²
#             (divide by 10,000 since 1 m² = 10,000 cm²)
# ------------------------------------------------------------

pressure_to_ISPPA <- function(P_kPa) {
  P_Pa    <- P_kPa * 1000              # Convert kPa → Pa
  I_Wm2   <- (P_Pa^2) / (2 * Z)       # I_SPPA in W/m²
  I_Wcm2  <- I_Wm2 / 10000            # Convert W/m² → W/cm²
  return(I_Wcm2)
}
```


```{r}
# ------------------------------------------------------------
# STEP 3: Function — compute dose (J/cm²) per Nandi et al.
# ------------------------------------------------------------
# Absorbed Dose = I_SPPA × DC × SD
#
# Where:
#   I_SPPA = spatial-peak pulse-average intensity (W/cm²)
#   DC     = duty cycle (unitless)
#   SD     = total sonication duration (s)
#
# Note: I_SPPA × DC = I_SATA (spatial-average temporal-average
#       intensity), so Dose = I_SATA × SD = J/cm²
# ------------------------------------------------------------

compute_dose <- function(I_SPPA_Wcm2, DC, SD_s) {
  I_SATA <- I_SPPA_Wcm2 * DC          # Temporal-average intensity (W/cm²)
  dose   <- I_SATA * SD_s             # Absorbed dose (J/cm²)
  return(list(I_SATA = I_SATA, dose = dose))
}
```


```{r}
# ------------------------------------------------------------
# STEP 4: Example — run across a range of pressures
# ------------------------------------------------------------

pressures_kPa_amcc_pcc <- subject_data$peak_pressure[subject_data$Region %in% c("aMCC", "PCC")]

cat("=== Pressure → I_SPPA Conversion ===\n")
cat(sprintf("%-15s %-20s\n", "Pressure (kPa)", "I_SPPA (W/cm²)"))
cat(strrep("-", 36), "\n")

for (P in pressures_kPa_amcc_pcc) {
  I <- pressure_to_ISPPA(P)
  cat(sprintf("%-15g %-20.4f\n", P, I))
}
```


```{r}
# ------------------------------------------------------------
# STEP 5: Dose calculation for both sonication durations
# ------------------------------------------------------------

cat("\n=== Dose Calculation (Nandi et al. framework) ===\n")
cat(sprintf("%-15s %-20s %-12s %-18s %-15s\n",
            "Pressure (kPa)", "I_SPPA (W/cm²)", "SD (s)",
            "I_SATA (W/cm²)", "Dose (J/cm²)"))
cat(strrep("-", 82), "\n")

results_verum <- data.frame()
SD_values <- 120
for (P in pressures_kPa_amcc_pcc) {
  I_SPPA <- pressure_to_ISPPA(P)
  for (SD in SD_values) {
    out <- compute_dose(I_SPPA, DC, SD)
    cat(sprintf("%-15g %-20.4f %-12g %-18.4f %-15.4f\n",
                P, I_SPPA, SD, out$I_SATA, out$dose))
    results_verum <- rbind(results_verum, data.frame(
      Pressure_kPa  = P,
      I_SPPA_Wcm2   = round(I_SPPA, 4),
      SD_s          = SD,
      I_SATA_Wcm2   = round(out$I_SATA, 4),
      Dose_Jcm2     = round(out$dose, 4)
    ))
  }
}
```
```{r}

# ------------------------------------------------------------
# STEP 4.2: SHAM run across a range of pressures
# ------------------------------------------------------------

pressures_kPa_sham <- subject_data$peak_pressure[subject_data$Region == "SHAM"]

cat("=== Pressure → I_SPPA Conversion ===\n")
cat(sprintf("%-15s %-20s\n", "Pressure (kPa)", "I_SPPA (W/cm²)"))
cat(strrep("-", 36), "\n")

for (P in pressures_kPa_sham) {
  I <- pressure_to_ISPPA(P)
  cat(sprintf("%-15g %-20.4f\n", P, I))
}
```
```{r}
# ------------------------------------------------------------
# STEP 5.2: Dose calculation for both sonication durations - SHAM
# ------------------------------------------------------------

cat("\n=== Dose Calculation (Nandi et al. framework) ===\n")
cat(sprintf("%-15s %-20s %-12s %-18s %-15s\n",
            "Pressure (kPa)", "I_SPPA (W/cm²)", "SD (s)",
            "I_SATA (W/cm²)", "Dose (J/cm²)"))
cat(strrep("-", 82), "\n")

results_sham <- data.frame()
SD_values  <- 2  # Sonication durations to evaluate (seconds)
for (P in pressures_kPa_sham) {
  I_SPPA <- pressure_to_ISPPA(P)
  for (SD in SD_values) {
    out <- compute_dose(I_SPPA, DC, SD)
    cat(sprintf("%-15g %-20.4f %-12g %-18.4f %-15.4f\n",
                P, I_SPPA, SD, out$I_SATA, out$dose))
    results_sham <- rbind(results_sham, data.frame(
      Pressure_kPa  = P,
      I_SPPA_Wcm2   = round(I_SPPA, 4),
      SD_s          = SD,
      I_SATA_Wcm2   = round(out$I_SATA, 4),
      Dose_Jcm2     = round(out$dose, 4)
    ))
  }
}
```

```{r}
# ------------------------------------------------------------
# STEP 6: Single-value quick-use wrapper
# ------------------------------------------------------------
# To use with your own pressure value, call:
#
#   P_kPa  <- 250          # <-- change to your value
#   I      <- pressure_to_ISPPA(P_kPa)
#   result <- compute_dose(I, DC, SD_s = 120)
#
#   cat(sprintf("I_SPPA : %.4f W/cm²\n", I))
#   cat(sprintf("I_SATA : %.4f W/cm²\n", result$I_SATA))
#   cat(sprintf("Dose   : %.4f J/cm²\n", result$dose))
# ------------------------------------------------------------

cat("\n=== Quick-use example: P = 250 kPa, SD = 120 s ===\n")
P_example <- 250
I_example <- pressure_to_ISPPA(P_example)
res_120   <- compute_dose(I_example, DC, SD_s = 120)
res_2     <- compute_dose(I_example, DC, SD_s = 2)

cat(sprintf("Pressure         : %g kPa\n",      P_example))
cat(sprintf("I_SPPA           : %.4f W/cm²\n",  I_example))
cat(sprintf("I_SATA           : %.4f W/cm²\n",  res_120$I_SATA))
cat(sprintf("Dose (SD = 2 s)  : %.4f J/cm²\n",  res_2$dose))
cat(sprintf("Dose (SD = 120s) : %.4f J/cm²\n",  res_120$dose))
cat(sprintf("Cumulative dose  : %.4f J/cm²\n",  res_2$dose + res_120$dose))
```
```{r}
results_uni <- bind_rows(results_verum, results_sham)

subject_data <- subject_data %>%
  mutate(row_id = row_number())

results_uni <- results_uni %>%
  mutate(row_id = row_number())

all_results <- left_join(subject_data, results_uni, by = "row_id") %>%
  select(-row_id)

save(all_results, file = "simulation_information_260309.RData") 
```

```{r}
ggpaired(all_results, x =  "Side", y = "I_SPPA_Wcm2" ,color = "Side",
     line.color = "grey", line.size = 0.3, id = "Subject", 
     facet.by = "Region", short.panel.labs = FALSE)

```

```{r}
ggpaired(all_results, x =  "Side", y = "Dose_Jcm2" ,color = "Side",
     line.color = "grey", line.size = 0.3, id = "Subject", 
     facet.by = "Region", short.panel.labs = FALSE)
```

# Load MODEL Data
```{r load-data}
# Load R.Data file containing modelRT
setwd("~/Documents/MediCoDe-TUS/Bayesian_learning-main")
load("ModelRT_prevAcc.RData")
load("ModelAcc_prevError.RData")


# Check modelRT structure
summary(modelRT)
```


## Extract Subject-Level Random Effects RT
```{r extract-random-effects}
ranef_subject <- ranef(modelRT)$Subject

# Helper function to extract random effects cleanly
extract_ranef <- function(ranef_obj, effect_name, col_prefix) {
  eff <- ranef_obj[, , effect_name]
  data.frame(
    Subject    = as.numeric(rownames(eff)),
    Estimate   = eff[, "Estimate"],
    Lower      = eff[, "Q2.5"],
    Upper      = eff[, "Q97.5"]
  ) %>% rename_with(~ paste0(col_prefix, .), -Subject)
}

# Extract the interaction effects of interest
stim1  <- extract_ranef(ranef_subject, "Stimulation1",  "Stim1_")
stim3  <- extract_ranef(ranef_subject, "Stimulation3",  "Stim3_")
stim1_cong  <- extract_ranef(ranef_subject, "Stimulation1:Congruence",  "Stim1_Congruence_")
stim3_cong  <- extract_ranef(ranef_subject, "Stimulation3:Congruence",  "Stim3_Congruence_")
stim1_block <- extract_ranef(ranef_subject, "Stimulation1:BlockTrnr_z", "Stim1_BlockTrnr_")
stim3_block <- extract_ranef(ranef_subject, "Stimulation3:BlockTrnr_z", "Stim3_BlockTrnr_")
stim1_prev  <- extract_ranef(ranef_subject, "Stimulation1:PrevError",   "Stim1_PrevError_")
stim3_prev  <- extract_ranef(ranef_subject, "Stimulation3:PrevError",   "Stim3_PrevError_")



# Combine all random effects into one data frame
model_subject_data <- stim1_cong %>%
  left_join(stim3_cong,  by = "Subject") %>%
  left_join(stim1_block, by = "Subject") %>%
  left_join(stim3_block, by = "Subject") %>%
  left_join(stim1_prev,  by = "Subject") %>%
  left_join(stim3_prev,  by = "Subject")%>%
  left_join(stim1,  by = "Subject")%>%
  left_join(stim3,  by = "Subject")

head(model_subject_data)
```


## Merge with Subject Data (keeping Region and Side separate)
```{r merge-data}
stim_info_dose <- all_results %>%
  group_by(Subject, Region) %>%
  summarise(Dose_mean = mean(Dose_Jcm2))
#show results
print(stim_info_dose)
# Keep Region and Side — do NOT aggregate across them
merged_data <- stim_info_dose %>%
  left_join(model_subject_data, by = "Subject") %>%
  filter(!is.na(Dose_mean))

# Check the data
head(merged_data)
print(paste("Total rows:", nrow(merged_data)))
```


## Helper: correlation + scatter plot function
```{r helper-function}
correlate_and_plot <- function(data, x_var, y_var, x_label, y_label, point_color = "steelblue") {
  cor_results <- data %>%
    group_by(Region) %>%
    summarise(
      n = sum(!is.na(.data[[x_var]]) & !is.na(.data[[y_var]])),
      r = cor(.data[[x_var]], .data[[y_var]], use = "complete.obs"),
      p_value = cor.test(.data[[x_var]], .data[[y_var]])$p.value,
      .groups = "drop"
    )
  print(cor_results)
  label_data <- cor_results %>%
    mutate(label = paste0("r = ", round(r, 3),
                          ", p = ", format.pval(p_value, digits = 2)))
  p <- ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_point(size = 3, alpha = 0.8, color = point_color) +
    geom_smooth(method = "lm", se = TRUE, color = point_color, fill = "lightblue") +
    geom_text(aes(label = Subject), vjust = -0.8, size = 2.8) +
    geom_text(data = label_data,
              aes(label = label),
              x = -Inf, y = Inf,
              hjust = -0.05, vjust = 3,
              inherit.aes = FALSE) +
    facet_grid(vars(Region)) +
    labs(
      title = paste0(y_label, " × ", x_label),
      x = x_label,
      y = y_label
    ) +
    theme_classic() +
    theme(
      axis.title.x = element_text(size = 16),
      axis.title.y = element_text(size = 16),
      axis.text.x  = element_text(size = 14),
      axis.text.y  = element_text(size = 14),
      legend.text  = element_text(size = 13),
      legend.title = element_text(size = 14),
      plot.title   = element_text(size = 18))
  print(p)
  invisible(cor_results)
}
```

## Correlations: Stimulation 1 and 3× Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1 Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3 Random Effect"
)
```

## Correlations: Stimulation1:Congruence × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_Congruence_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1:Congruence Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_Congruence_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3:Congruence Random Effect"
)
```
## Correlations: Stimulation1:BlockTrnr × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_BlockTrnr_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1:BlockTrnr Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_BlockTrnr_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3:BlockTrnr Random Effect"
)
```

## Correlations: Stimulation1:PrevError × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_PrevError_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1:PrevError Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_PrevError_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3:PrevError Random Effect"
)
```




## peak_pressure


## Merge with Subject Data (keeping Region and Side separate)
```{r merge-data}
stim_info_dose_isppa <- all_results %>%
  group_by(Subject, Region) %>%
  summarise(isppa_mean = mean(I_SPPA_Wcm2))
#show results
print(stim_info_dose_isppa)
# Keep Region and Side — do NOT aggregate across them
merged_data_isppa <- stim_info_dose_isppa %>%
  left_join(model_subject_data, by = "Subject") %>%
  filter(!is.na(isppa_mean))

# Check the data
head(merged_data_isppa)
print(paste("Total rows:", nrow(merged_data_isppa)))
```
## Correlations: Stimulation1 & 3 × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1 Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3 Random Effect"
)
 
```
## Correlations: Stimulation1:Congruence × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_Congruence_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1:Congruence Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_Congruence_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3:Congruence Random Effect"
)
```
## Correlations: Stimulation1:BlockTrnr × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_BlockTrnr_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1:BlockTrnr Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_BlockTrnr_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3:BlockTrnr Random Effect"
)
```

## Correlations: Stimulation1:PrevError × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_PrevError_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1:PrevError Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_PrevError_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3:PrevError Random Effect"
)
```


## Correlation ACCURACY - ISPPA

```{r load-data}
summary(modelAcc)

```

## Extract Subject-Level Random Effects Acc
```{r extract-random-effects}
ranef_subject <- ranef(modelAcc)$Subject

# Helper function to extract random effects cleanly
extract_ranef <- function(ranef_obj, effect_name, col_prefix) {
  eff <- ranef_obj[, , effect_name]
  data.frame(
    Subject    = as.numeric(rownames(eff)),
    Estimate   = eff[, "Estimate"],
    Lower      = eff[, "Q2.5"],
    Upper      = eff[, "Q97.5"]
  ) %>% rename_with(~ paste0(col_prefix, .), -Subject)
}

# Extract the interaction effects of interest
stim1  <- extract_ranef(ranef_subject, "Stimulation1",  "Stim1_")
stim3  <- extract_ranef(ranef_subject, "Stimulation3",  "Stim3_")
stim1_cong  <- extract_ranef(ranef_subject, "Stimulation1:Congruence",  "Stim1_Congruence_")
stim3_cong  <- extract_ranef(ranef_subject, "Stimulation3:Congruence",  "Stim3_Congruence_")
stim1_block <- extract_ranef(ranef_subject, "Stimulation1:BlockTrnr_z", "Stim1_BlockTrnr_")
stim3_block <- extract_ranef(ranef_subject, "Stimulation3:BlockTrnr_z", "Stim3_BlockTrnr_")
stim1_prev  <- extract_ranef(ranef_subject, "Stimulation1:PrevError",   "Stim1_PrevError_")
stim3_prev  <- extract_ranef(ranef_subject, "Stimulation3:PrevError",   "Stim3_PrevError_")

# Combine all random effects into one data frame
model_subject_data_acc <- stim1_cong %>%
  left_join(stim3_cong,  by = "Subject") %>%
  left_join(stim1_block, by = "Subject") %>%
  left_join(stim3_block, by = "Subject") %>%
  left_join(stim1_prev,  by = "Subject") %>%
  left_join(stim3_prev,  by = "Subject") %>%
  left_join(stim1,  by = "Subject") %>%
  left_join(stim3,  by = "Subject")

head(model_subject_data)
```


## Merge with Subject Data (keeping Region and Side separate)
```{r merge-data}
stim_info_dose <- all_results %>%
  group_by(Subject, Region) %>%
  summarise(Dose_mean = mean(Dose_Jcm2))
#show results
print(stim_info_dose)
# Keep Region and Side — do NOT aggregate across them
merged_data <- stim_info_dose %>%
  left_join(model_subject_data_acc, by = "Subject") %>%
  filter(!is.na(Dose_mean))

# Check the data
head(merged_data)
print(paste("Total rows:", nrow(merged_data)))
```
## DOSE

## Correlations: Stimulation1 and 3 × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1 Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3 Random Effect"
)
```

## Correlations: Stimulation1:Congruence × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_Congruence_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1:Congruence Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_Congruence_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3:Congruence Random Effect"
)
```
## Correlations: Stimulation1:BlockTrnr × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_BlockTrnr_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1:BlockTrnr Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_BlockTrnr_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3:BlockTrnr Random Effect"
)
```

## Correlations: Stimulation1:PrevError × Dose
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "aMCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim1_PrevError_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim1:PrevError Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data, Region == "PCC"),
  x_var   = "Dose_mean",
  y_var   = "Stim3_PrevError_Estimate",
  x_label = "Dose (J/cm2)",
  y_label = "Stim3:PrevError Random Effect"
)
```




## ISPPA


## Merge with Subject Data (keeping Region and Side separate)
```{r merge-data}
stim_info_dose_isppa <- all_results %>%
  group_by(Subject, Region) %>%
  summarise(isppa_mean = mean(I_SPPA_Wcm2))
#show results
print(stim_info_dose_isppa)
# Keep Region and Side — do NOT aggregate across them
merged_data_isppa <- stim_info_dose_isppa %>%
  left_join(model_subject_data_acc, by = "Subject") %>%
  filter(!is.na(isppa_mean))

# Check the data
head(merged_data_isppa)
print(paste("Total rows:", nrow(merged_data_isppa)))
```
## Correlations: Stimulation1 × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1 Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3 Random Effect"
)
```

## Correlations: Stimulation1:Congruence × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_Congruence_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1:Congruence Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_Congruence_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3:Congruence Random Effect"
)
```
## Correlations: Stimulation1:BlockTrnr × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_BlockTrnr_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1:BlockTrnr Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_BlockTrnr_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3:BlockTrnr Random Effect"
)
```

## Correlations: Stimulation1:PrevError × ISPPA
```{r cor-stim1-cong}
cor_stim1_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "aMCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim1_PrevError_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim1:PrevError Random Effect"
)

cor_stim3_cong <- correlate_and_plot(
  data    = filter(merged_data_isppa, Region == "PCC"),
  x_var   = "isppa_mean",
  y_var   = "Stim3_PrevError_Estimate",
  x_label = "Isppa (W/cm2)",
  y_label = "Stim3:PrevError Random Effect"
)
```

